A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-22 paper/refactor.tex
add and standarize bibliography. also fix typos

\author{Leonardo Lazzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Julián Peller,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Juan Manuel Pérez,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
}

%&\contributor{Submitted to Proceedings of the National Academy of Sciences
%of the United States of America}

@@

We selected some starred works from Lenin from the "Marxists Internet Archive"\cite{LENIN}. Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economy essay called ``Imperialism, the highest stage of capitalism''.

@@

The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Wu-Palmer similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity. The former three are analytical, this is, their calculus is based only in the semantic relations of the thesaurus, meanwhile, the last three are analytical but also use statistics from a corpus.\cite{BUDANITSKY}\cite{BUDANITSKY_2}. In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one). Path similarity was the best in the trade off between the complexity of the measure and the obtained results. This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.

@@

\begin{thebibliography}{10}
\bibitem{LENIN}
Marxists Internet Archive, {\em www.marxists.org} %, No estaria pudiendo definir bien esta referencia
\bibitem{DARWIN}
M.A. Montemurro and D. H. Zanette, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
\bibitem{ENTROPIC}
M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
\bibitem{MAS-ZANETTE}
\bibitem{WORDNET}
George A. Miller, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
\bibitem{LESK}
M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.
\bibitem{BUDANITSKY}
Evaluating WordNet-based Measures of Lexical Semantic Relatedness
http://aclweb.org/anthology//J/J06/J06-1003.pdf
\bibitem{BUDANITSKY_2}
Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures
ftp://learning.cs.utoronto.ca/pub/gh/Budanitsky+Hirst-2001.pdf
\end{thebibliography}
\end{article}
\end{document}

>>>>

\author{Leonardo Lazzaro\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Julián Peller\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Juan Manuel Pérez\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina}
}

@@

We selected some starred works from Lenin from the "Marxists Internet Archive"\cite{LENIN}. Those works are very different in topic, some of them being strictly phylosophical essays (such as ``Materialism and Empiriocriticism'') and other being more political, such as ``State and Revolution'', and finally an economic essay called ``Imperialism, the highest stage of capitalism''.

@@

The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Wu-Palmer similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity. The former three are analytical, this is, their calculus is based only in the semantic relations of the thesaurus, meanwhile, the last three are analytical but also use statistics from a corpus.\cite{BUDANITSKY}\cite{BUDANITSKY_2}. In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one). This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.

@@

\begin{thebibliography}{10}
\bibitem{LENIN}
Marxists Internet Archive (\url{http://www.marxists.org})
\bibitem{DARWIN}
M.A. Montemurro \& D. H. Zanette, 2009, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
\bibitem{ENTROPIC}
M.A. Montemurro \& D. H. Zanette, 2001, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems Vol. 5, September 27th 2001
\bibitem{MAS-ZANETTE}
M.A. Montemurro \& D. H. Zanette, 2010, {\em Towards the quantification of the semantic information encoded in written language}, Adv. Complex Systems Vol. 13.
\bibitem{WORDNET}
George A. Miller, 1995, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
\bibitem{LESK}
M. Lesk., 1986, {\em Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone}. In Proceedings of SIGDOC ’86.
\bibitem{BUDANITSKY}
Budanitsky \& Hirst, 2004, {\em Evaluating WordNet-based Measures of Lexical Semantic Relatedness}
%\url{http://aclweb.org/anthology//J/J06/J06-1003.pdf}
\bibitem{BUDANITSKY_2}
Budanitsky \& Hirst, 2001, {\em Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures}
%\bibitem{SLEZAK}
%C. Diuk, D. Slezak et al., 2013, {\em A quantitative philology of introspection}, Frontiers in Integrative Neuroscience Vol. 8
\end{thebibliography}
\end{article}
\end{document}
